---
title: "An overview of pQTLdata"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
author:
  - Department of Public Health and Primary Care
  - University of Cambridge
  - Cambridge, UK
  - https://jinghuazhao.github.io/
date: '`r Sys.Date()`'
bibliography: refs.bib
vignette: >
  %\VignetteIndexEntry{pQTLdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
set.seed(0)
knitr::opts_chunk$set(
  out.extra = 'style="display:block; margin: auto"',
  fig.align = "center",
  fig.path = "pQTLdata/",
  collapse = TRUE,
  comment = "#>",
  dev = "png")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pkgs <- c("knitr")
for (p in pkgs) if (length(grep(paste("^package:", p, "$", sep=""), search())) == 0) {
    if (!requireNamespace(p)) warning(paste0("This vignette needs package `", p, "'; please install"))
}
invisible(suppressMessages(lapply(pkgs, require, character.only = TRUE)))
```

This package intends to gather information on meta-data and relevant scripts in proteogenomic analysis.

# Collections

As used in several years of proteomic analysis and for future extensions, the collections are in two locations:

1. **`data/`**. R datasets.
2. **`inst/`**. `EndNote/`, `Olink/`, `scripts/`, `pQTLdata.sh`, `docs.sh` which spread into the package's root directory after installation.

While `library(help=pQTLdata)` displays the general information, `? pQTLdata` can give a list of data object in the package.

# Protein panels

The Olink qPCR inflammation panel (`inf1`) used in the SCALLOP consortium seeds the collection.

```{r inf1, echo=FALSE}
options(width=200)
knitr::kable(pQTLdata::inf1,caption="Olink/inflammation panel")
```

followed by inclusion of Olink_qPCR for all 12 panels, Olink NGS, Caprion and SWATH-MS panels. `SomaScanV4.1` is directly from SomaLogic.

It is of interest to compare some of these,

```{r, echo=FALSE, fig.cap="Overlap of Olink Explore HT, SomaLogic V4.1 and Caprion", fig.height=9, fig.width=9, messages=FALSE, results="hide"}
suppressMessages(library(dplyr))
suppressMessages(library(VennDiagram))
uniprot <- list(Olink=pull(pQTLdata::Olink_Explore_HT,UniProt.ID),
                Somalogic=pull(pQTLdata::SomaScanV4.1,UniProt.ID),
                Caprion=pull(pQTLdata::caprion,Accession))
lapply(uniprot,head)
olink_somalogic_caprion <- VennDiagram::venn.diagram(uniprot,filename = NULL,disable.logging = TRUE,
                                                     cex = 2.5, cat.cex = 2.5, cat.pos = c(0,0,180),
                                                     height=8,width=8,units="in")
grid.newpage()
grid.draw(olink_somalogic_caprion)
```

# Published data

This associates with the analysis of INTERVAL data as reported by @sun18, which includes the panel `SomaLogic160410`, supplementary tables 4, 6, 18.

# Reference data

Extractions `biomaRt`, `hg19` and `hg19Tables` are based on ENSEMBL BioMart and UCSC.

# Scripts

An analysis involving COVID-19 data is in `Olink/` directory , while the `scripts/` directory records data generation which potentially can be extended.

Specifically, `pQTLdata.sh` handles package under Cambridge Service for Data Driven Discovery (CSD3) system, and `docs.sh` operates with GitHub.

# URLs

- Cell Carta, <https://cellcarta.com/>
- EndNote, <https://endnote.com/>
- ENSEMBL BioMart, <https://www.ensembl.org/index.html>
- GitHub, <https://github.com/>
- INTERVAL study, <http://www.donorhealth-btru.nihr.ac.uk/studies/interval-study/>
- NULISA, <https://alamarbio.com/technology/nulisa-platform/>
- Olink, <https://olink.com/>
- SCALLOP consortium, <http://www.scallop-consortium.com/>
- SomaLogic, <https://somalogic.com/>
- SWATH-MS, <https://www.creative-proteomics.com/ngpro/swath-ms.html>
- UCSC, <https://genome.ucsc.edu/>

# References {-}

The `EndNote/` directory includes references in @sun18 and @suhre20 formatted in EndNote.
