---
title: "An overview of pQTLdata"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    check_title: false
bibliography: refs.bib
vignette: >
  %\VignetteIndexEntry{pQTLdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
set.seed(0)
knitr::opts_chunk$set(
  out.extra = 'style="display:block; margin: auto"',
  fig.align = "center",
  fig.path = "pQTLdata/",
  collapse = TRUE,
  comment = "#>",
  dev = "png")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pkgs <- c("knitr")
for (p in pkgs) if (length(grep(paste("^package:", p, "$", sep=""), search())) == 0) {
    if (!requireNamespace(p)) warning(paste0("This vignette needs package `", p, "'; please install"))
}
invisible(suppressMessages(lapply(pkgs, require, character.only = TRUE)))
```

## An overview

Collections in in this package are in two subdirectories

1. **data**/, which contains R objects.
2. **inst**/, which contains `csd3.sh`, `docs.sh`, EndNote/, Olink/, scripts/ that will spread into the package's root directory after installation.

## Protein panels

The Olink qPCR inflammation panel (`inf1`) used in the SCALLOP consortium seeds the collection.

```{r inf1, echo=FALSE}
options(width=200)
knitr::kable(pQTLdata::inf1,caption="Table 1. Olink/inflammation panel")
```

This is later extended to include all 12 Olink qPCR panels, Olink NGS, Caprion and SWATH-MS panels. `SomaScanV4.1` is directly from SomaLogic.

## Published data

This is notably the analysis of INTERVAL data as reported by @sun18, which includes the panel `SomaLogic160410`, supplementary tables 4, 6, 18.

## Reference data

These include `biomaRt`, `hg19` and `hg19Tables` from BioMART and UCSC.

## Scripts

Files `csd3.sh` and `docs.sh` handle package under Cambridge University's CSD3 system and GitHub, respectively.

The `scripts/` directory records data generation which potentially can be extended.

Directory `Olink/` contains an analysis involving COVID-19 data.

## References

The collection with EndNote/ includes references in @sun18 and @suhre20 are EndNote libraries.
